Named Entity Recognition as Structured Prediction

### 2012-11-11 doc/report/paper.tex
Tables, stuff.

\begin{abstract}
In this paper, we apply the method of structure prediction to the information extraction task: Named Entity Recognition (NER). 
We illustrate a number issues relevant to the NER task, describe our implementation and compare it to state-of-the art methods.
%We use a structured version of the Perceptron algorithm with averaging and Viterbi decoding.
\end{abstract}

@@

\begin{table}[h!]
\small
\begin{tabular}{ l | l }

@@

\begin{table}[h!]
\scriptsize
\begin{tabular}{|l|l|l|l|}
\hline
\bf Language & \bf Precision & \bf Recall & \bf $F_1$-measure \\ \hline
Spanish &             26.27\% & 56.48\% & 35.86\%        \\
Dutch  &             64.38\%  &45.19\%    & 53.10\%  \\
English &              71.91\%& 50.90\%  & 59.61 $\pm$ 1.2\%\\
German &      31.86\%  & 28.89\% & 30.30  $\pm$ 1.3\% \\
\hline
\end{tabular}
\caption{NER Baseline}
\label{table:Base}
\end{table}

@@

\begin{table}[h!]
\begin{tabular}{ l | l }
\bf Feature & \bf Example \\
\hline
Token &  \textbf{``Amsterdam''}\\
Suffix& Amster\textbf{dam}\\
Prefix&  \textbf{San} Sebastian\\
Captitalized& \textbf{B}enetton\\
Number Pattern & \\
UPPERCASE &  \textbf{BENETTON}\\
POS-tag &  Benetton \textbf{NNP}   \\
Lemma &  produced $\Rightarrow$ produce \\

>>>>

\begin{abstract}
In this paper, we apply the method of structure prediction to the Named Entity Recognition (NER) information extraction task. 
We illustrate a number of issues relevant to the NER task, describe our implementation and compare it to state-of-the art methods.
%We use a structured version of the Perceptron algorithm with averaging and Viterbi decoding.
\end{abstract}

@@

\begin{table}[h!]
\scriptsize
\begin{tabular}{ l l }

@@

\begin{table}[h!]
\small
\begin{tabular}{|l|l|l|l|}
\hline
\bf Language & \bf Precision & \bf Recall & \bf $F_1$-measure \\ \hline
Spanish &             26.27\% & 56.48\% & 35.86\%        \\
Dutch  &             64.38\%  &45.19\%    & 53.10\%  \\
English &              71.91\%& 50.90\%  & 59.61 $\pm$ 1.2\%\\
German &      31.86\%  & 28.89\% & 30.30  $\pm$ 1.3\% \\
\hline
\end{tabular}
\caption{Named Entity Recognition baselines.}
\label{table:Base}
\end{table}

@@

\begin{table}[h!]
\small
\begin{tabular}{ l l }
\bf Feature & \bf Example \\
\hline
Token &  \textbf{``Amsterdam''}\\
Suffix& Amster\textbf{dam}\\
Prefix&  \textbf{San} Sebastian\\
Captitalized& \textbf{B}enetton\\
Number Pattern & \\
UPPERCASE &  \textbf{BENETTON}\\
POS-tag &  Benetton \textbf{NNP}   \\
Lemma &  produced $\Rightarrow$ produce \\
